%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Licencia :                                                 %
%     GNU FDL                                                  %
%                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,fleqn,a4]{book}
%   Makeindex support
\usepackage{makeidx}
\makeindex
%   Usual document characteristics
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cursomo}


\begin{document}
\lstset{language=Octave}
\title{\begin{Huge}Curso de Octave para la docencia en la
    UCA\end{Huge}\\ Material de apoyo al curso.}


\author{Guillem Borrell i Nogueras\\
  \texttt{\url{http://iimyo.forja.rediris.es/}}\\
}

\maketitle


Este documento está publicado según la siguiente licencia:
\begin{center}
\begin{Huge}
GNU Free Documentation License
\end{Huge}

\end{center}

\bigskip
\begin{quote}
    Copyright \copyright{}  2008  GUILLEM BORRELL I NOGUERAS.
    Permission is granted to copy, distribute and/or modify this document
    under the terms of the GNU Free Documentation License, Version 1.2
    or any later version published by the Free Software Foundation;
    with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
    A copy of the license is included in the section entitled ``GNU
    Free Documentation License''.
\end{quote}

Matlab${\textregistered}$ y MathWorks${\textregistered}$ son nombres
registrados por MathWorks\\


\tableofcontents{}

\listoffigures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\input{intro.tex}
\input{matlab.tex}

\begin{thebibliography}{99}

\bibitem{Turbulence}

  Turbulence and Vortex Dynamics; Javier Jiménez; July 26, 2004;
  \url{http://torroja.dmt.upm.es/}

\bibitem{Fortran}

  Fortran 95/2003 Explained; Michael Metcalf, John Reid, Malcolm
  Cohen; Oxford University Press; 2004.

\bibitem{Numerical}

  Numerical Recipes in Fortran 77, The Art of Scientific Computing;
  Second Edition; William H. Press, Saul A. Teukolsky, William T.
  Vetterling, Brian P. Flannery; Cambridge University Press, 1997

\bibitem{Orlandi}

  Fluid Flow Phenomena, A Numerical Toolkit; Paolo Orlandi; Kluwer
  Academic Publishers, 2000.

\bibitem{Chung}

  Computational Fluid Dynamics; T.S. Chung; Cambridge University
  Press, 2002

\bibitem{Schildt}

  C++: The Complete Reference; Herbert Schildt; Tata Mc Graw-Hill
  ,1999

\bibitem{OctaveWiki}

  Scary Octave; \url{http://wiki.octave.org/}

\bibitem{OctaveManual}

  The Octave Language for Numerical Computations; John W. Eaton;
  \url{http://www.octave.org/}

\bibitem{Python}

  Python Tutorial; Guido van Rossum;
  \url{http://www.python.org/tut/tut.html}

\bibitem{Wolfram}

  MathWorld; Eric W. Weisstein; \url{http://mathworld.wolfram.com/}

\bibitem{Fluidos}

  Mecánica de Fluidos; Amable Liñán; Publicaciones ETSIA, Universidad
  Politécnica de Madrid.

\bibitem{Numerico1}

  Cálculo Numérico I; Varios; Publicaciones ETSIA, Universidad
  Politécnica de Madrid.

\bibitem{EDO}

  Análisis y Cálculo Numérico en Ecuaciones en Derivadas Parciales;
  Juan A. Hernández, Eusebio Valero; Publicaciones ETSIA, Universidad
  Politécnica de Madrid.

\bibitem{Trefethen}

  Spectral methods in MATLAB; Lloyd N. Trefethen; SIAM, 2000

\bibitem{Algebra}

  Algebra Lineal y Geometría Cartesiana; Juan de Burgos; McGraw Hill,
  2000

\bibitem{Multicapa}

  Fortran 95; Programación Multicapa para la simulación de sistemas
  físicos; Juan A. Hernández, Mario A. Zamecnik; ADI, 2001.

\bibitem{Wikipedia}

  Wikipedia, the free
  encyclopedia:\url{http://en.wikipedia.org/wiki/Wikipedia}

\bibitem{Dijkstra}

  The Humble Programmer; Edsger W. Dijkstra;
  \url{http://www.cs.utexas.edu/~EWD/transcriptions/EWD03xx/EWD340.html}

\bibitem{Boyd}
  Chebyshev and Fourier Spectral Methods; J. P. Boyd
  \url{http://laplace.physics.ubc.ca/People/jason/references/Boyd_2ed.pdf}

\bibitem{Numpy}
  Guide to NumPy; Travis E. Oliphant; \url{http://scipy.org/}

  



\end{thebibliography}





\printindex{}

\end{document}
